%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Working Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Engineer, Custom Design Flow Development Department, Design Technology Platform (DTP), R\&D} % Job title
    {Taiwan Semiconductor Manufacturing Company (TSMC)} % Organization
    {Hsinchu, Taiwan} % Location
    {Jul. 2021 - Jul. 2024} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Built a \textbf{delay calculator}, which takes DSPF as input and calculates the timing within a standard cell. 
        The tool is 10-100x faster than commercial tool without license while maintaining >0.9 correlation.
        % This in-house method is more than \ul{10x faster} for delay or \ul{100x faster} for setup time than conventional spice simulation without commercial licenses while maintaining \ul{more than 0.9} of the ranking correlation coefficient.
        % \item Built a \textbf{fully automated flow} to verify silicon photonics process design kit (PDK). With the help of my programming expertise and computer system knowledge, the speed of the whole process is \ul{20x faster} than a record-and-replay method using GUI.
        \item Build a \textbf{fully automated flow} for process design kit (PDK) quality check, covering pre-sim, layout, LVS, DRC, RCX. \ul{20x speedup} is observed than traditional manual flow.
        \item Designed and maintained an \textbf{Automatic Quality Checking (QC) system} that runs specified scripts and generates an HTML report. This system assures developers and managers that the latest code can function as expected without them having to run their tests.
        % \item Having written miscellaneous parsers including spice, verilog, lef, etc., and am acquainted with regular expression.
        \item Related tools: Virtuoso, HSPICE, Calibre, Custom Compiler, IC Validator, Innovus, StarRC, ADE, PrimeWave
        \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Part-time worker, Division of Network Management, Computer \& Information Networking Center}
    {National Taiwan University}
    {Taipei, Taiwan}
    {Apr. 2018 - Jan. 2021}
    {
        \begin{cvitems}
        \item Built and maintained \textbf{VisQWL}: a \ul{Vis}ualization framework for monitoring the \ul{Q}uality of campus-wide \ul{W}ire\ul{L}ess service. The heat map can easily pinpoint the hot spot of Wi-Fi usage, guide the system administrators about resource arrangement, and provide a tool to deal with user complaints.
        \item Skills: SNMP, Kibana, Elasticsearch, data visualization, wireless network, map data processing
        \item The work was published in a regional conference \href{https://tanet2020.ntu.edu.tw/index30.php}{TANet30}, and is online serving at \href{https://ccnet.ntu.edu.tw/wireless/}{https://ccnet.ntu.edu.tw/wireless/} (Chinese only)
        \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
