%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activities \& Leadership \& Teaching}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Long-term Support and Senior Consultant/Leader} % Affiliation/role
    {Equipment Team, NTU Tainan Alumni Association (TAA)} % Organization/group
    {Taipei, Taiwan} % Location
    {Jul. 2015 - Apr. 2021} % Date(s)
    {
        \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item This team is responsible for all the hardware for hosting stage performances. The equipment comes in four major fields: stage lighting, public address (PA) system, photography, and video recording. 
        \item Having mastered all four fields, I coordinated the crew assigned with various responsibilities and made sure they could 1) have smooth communication with performers before the event, 2) set up the equipment within often tight time budget, and 3) correctly operate the devices to meet the performers' requirements.
        \item Leading and training the staff of this team whose personnel is replenished on a yearly basis. My apprentices span over 6 generations
        \item Designed technical lectures and hands-on training to teach newcomers so that they can work independently during real events. I have taught at least 10+ lectures in this group.
        \item Built up a sustainable lecture and training framework that can be passed down for generations even after I left NTU
        \item I have a series of documentary videos on this team in my \href{https://www.youtube.com/channel/UCI6m_87ud6TXVhVh4o-NOMg}{YouTube channel}
        \end{cvitems}
    }
%---------------------------------------------------------

  \cventry
    {Network Administrator and Director of Equipment} % Affiliation/role
    {NTU Public Address (PA) Team} % Organization/group
    {Taipei, Taiwan} % Location
    {Sep. 2017 - Aug. 2018} % Date(s)
    {
        \begin{cvitems} % Description(s) of experience/contributions/knowledge
        % \item Built a radius server for members to exploit WPA2 enterprise-grade Wi-Fi so that the shared network is more secure and easier to manage. 
        \item Built a radius server so that the shared Wi-Fi could be more secure, manageable, and traceable.
        \item Enhanced the logging system to better handle network security events.
        \item Managing, maintaining, and purchasing new equipment for this team
        \item Taught 7 lectures, including ``Decibel and Phase'' (3 times), ``Introduction to the Systems in the Auditorium'', ``Introduction to the Network System of PA Team'', ``Introduction to X32 (a digital mixer)'', ``Introduction to Photography''
        \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Coach} % Affiliation/role
    {NTUEE badminton department team} % Organization/group
    {Taipei, Taiwan} % Location
    {Sep. 2017 - Jan. 2021} % Date(s)
    {
        \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item Taught new members badminton skills and served balls to them.
        \item Taught experienced members tactics about the plays and pointed out their weaknesses and possible ways of improvement.
        \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Event General Coordinator} % Affiliation/role
    {Night of NTU Tainan Alumni Association} % Organization/group
    {Taipei, Taiwan} % Location
    {Oct. 2015 - Mar. 2016} % Date(s)
    {
        \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item Ranked as one of the top three nights in NTU, famous for its high-quality drama, this event consists of about 80 drama performers, 20 dancers, and 70 workers. I was one of the three highest leaders of this event.
        \item The main responsibility was to arrange resources and the schedule to ensure the event could be held successfully
        \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
